Is structure based drug design ready for selectivity optimization?

### 2018-12-19 manuscript.tex
first pass of the results section

\paragraph{The CDK2 and CDK9 experimental dataset demonstrates the difficulty in achieving selectivity for closely related kinases}

To begin quantifying the correlation of errors in free energy predictions for selectivity, we set out to gather datasets that met a number of criteria. We looked for datasets that contained binding affinity data for a number of kinase targets and ligands, as well as having crystal structures for each target with the same co-crystallized ligand. For the CDK2/CDK9 datatset~\citep{Shao2013-oe}, ligand 12c was cocrystallized with CDK2/cylin A (Figure~\ref{fig:figure-2}A, left) and CDK9/cyclin T (Figure~\ref{fig:figure-2}B, left), work that was published in a companion paper~\citep{Hole2013-sr}. In both CDK2 and CDK9, ligand 12c forms relatively few hydrogen bond interactions with the kinase. Each kinase forms a set of hydrogen bonds between the ligand scaffold and a hinge residue (C106 in CDK9 and L83 in CDK2) that is conserved across all of the ligands in this series. CDK9, which has slightly lower affinity for ligand 12c (Figure~\ref{fig:figure-2}C, right), forms a lone interaction between the sulfonamide of ligand 12c and residue E107. On the other hand, CDK2 forms interactions between the sulfonamide of ligand 12c and residues K89 and H84. The congeneric series of ligands contains a number of challenging perturbations, particularly at substituent point R3 (Figure~\ref{fig:figure-2}C, left). Ligand 12i also presented a challenging perturbation, moving the 1-(piperazine-1-yl)ethanone from the \emph{meta} to \emph{para} location.

@@

\paragraph{The CDK2 and ERK2 dataset achieves higher levels of selectivity for more distantly related kinases}
\todo{I probably need to either remove the reference to how closely related the kinases are, or come up with a way to quantify that - SKA}
The CDK2/ERK2 datatset from Blake \emph{et al.,} 2016 also met the criteria described above. Crystal structures for both CDK2 (Figure~\ref{fig:figure-3}A, top) and ERK2 (Figure~\ref{fig:figure-3}B, top) were available with ligand 22 co-crystallized. Of note, CDK2 was not crystallized with cyclin A, despite cyclin A being included in the affinity assay reported in the paper~\citep{Blake2016-su}. CDK2 adopts a DFG-in conformation with the $\alpha$C helix rotated out, away from the ATP binding site and breaking the conserved salt bridge between K33 and E51 (Supp. Figure~\ref{fig:sup-figure-1}A), indicative of an inactive kinase~\citep{Huse2002-ml,Hari:2013dp}. By comparison, the CDK2 structure from the CDK2/CDK9 dataset adopts a DFG-in conformation with the $\alpha$C helix rotated in, forming the ionic bond between K33 and E51 indicative of an active kinase, due to allosteric activation by cyclin A. While missing cyclins have caused problems for free energy calculations in prior work~\todo{is there a good citation for this?}, it is possible that the fully active conformation contributes equally to binding affinity for all of the ligands in the series, and the high accuracy of the potency predictions (Figure~\ref{fig:figure-4}, top left) is the result of fortutious cancellation of errors. The binding mode for this series is similar between both kinases. There is a set of conserved hydrogens bonds between the scaffold of the ligand and the backbone of one of the hinge residues (L83 for CDK2 and M108 for ERK2). The conserved lysine (K33 for CDK2 and K54 for ERK2), normally involved in the formation of a ionic bond with the $\alpha$C helix, forms a hydrogen bond with the scaffold (Figure~\ref{fig:figure-4}A and~\ref{fig:figure-4}B, bottom) in both CDK2 and ERK2. However, in the ERK2 structure, the hydroxyl engages a crystallographic water as well as N154 in a hydrogen bond network that is not present in the CDK2 structure. 
The congenric ligand series features a single subsituent point, with the R groups exposed to the solvent. This helps explain the extremely narrow distribution of selectivities, with a mean selectivity of -1.74 kcal/mol (ERK2 - CDK2) and standard deviation of 0.56 kcal/mol. This suggests that the selectivity is largely driven by the scaffold and unaffected by the R group substitutions.

@@

\paragraph{FEP+ calculations show accurate potency predictions for ERK2/CDK2 and larger errors for CDK2/CDK9}
The FEP+ predictions of single target potencies ($\Delta G$) showed good accuracy for the CDK2 and ERK2 dataset (Figure~\ref{fig:figure-4}, top), with an RMSE of $0.37^{0.57}_{0.16}$ and $0.53^{0.81}_{0.22}$ kcal/mol, respectively. All of the CDK2 and ERK2 potencies were predicted within 1 log unit of the experimental value. The selectivity ($\Delta \Delta G_{selectivity}$) predictions show an RMSE of $0.81^{1.26}_{0.37}$ kcal/mol, with all of the predictions falling within 1 log unit of the experimental values (Figure~\ref{fig:figure-4}, top right panel).\todo{this will change if we take of the ff uncertainty error bars}. Despite the high accuracy of the predictions, the narrow dynamic range and high uncertainty from experiment and calculation obscures any signal in the data. 
The CDK2 and CDK9 datasets show higher errors in the potency predictions, with an RMSE of $1.39^{2.05}_{0.58}$ and $1.71^{2.61}_{0.61}$ kcal/mol respectively. There are a number of outliers that fall outside of 1 log unit from the experimental value. While the higher per target errors make predicting potency more difficult, the selectivity predictions show a much lower RMSE of $0.74^{1.25}_{0.31}$ kcal/mol. This suggests that some correlation in the error is leading to fortuitous cancellation of systematic error, leading to more accurate than expected predictions of $\Delta \Delta G_{selectivity}$.

@@

\paragraph{Correlation of forcefield errors accelerates selectivity optimization}
To quantify the correlation coefficient ($
\rho$) of the forcefield errors in our calculations, we built a Bayesian graphical model to separate the forecefield error from the statistical error, as described in the methods section. Briefly, we modeled the absolute free energy ($G$) of each ligand in each phase (complex and solvent) as in equation~\ref{eq4}. The model was chained to the FEP+ calculations by providing the $\Delta G^{calc}_{phase,ij,target}$ as observed data, as in equation~\ref{eq6}. As in equation, the experimental data was modeled as a normal distribution centered around the true free energy of binding ($\Delta G^{true}_{i,target}$) corrupted by experimental error, which is assumed to be 0.3 kcal/mol from previous work done to quantify the uncertainty in publicly available data~\citep{BROWN2009420}. The reported IC50 values from each dataset were treated as data observations (Equation~\ref{eq12}) and the $\Delta G^{true}_{i,target}$ was assigned a weak normal prior (Equation~\ref{eq13}). The correlation coefficient was calculated for each sample according to equation~\ref{eq9}. 
The correlation coefficient $\rho$ for the CDK2/ERK2 calculations was quantified to be $0.5^{0.33}_{-0.23}$, indicating that the errors are largely uncorrelated between ERK2 and CDK2 (Figure~\ref{fig:figure-5}A, right). The joint marginal distribution of the error ($\epsilon$) for each target is symmetric, which is expected for cases in which $\rho$ is 0 (Supp. Figure~\ref{fig:sup-figure-2}). Despite the weak correlation in errors, the high per target accuracy of these calculations should have a 2-3x speed up for 1 log unit selectivity optimization, and a 20-30x speed up for 2 log unit selectivity optimization (Figure~\ref{fig:figure-5}A, right). 
The CDK2/CDK9 calculations show strong evidence of correlation, with a correlation coefficient of $0.70^{0.82}_{0.57}$ (Figure~\ref{fig:figure-5}B, right). The joint marginal distribution of errors is strongly diagonal, which is expected based on the value for $\rho$ (Figure~\ref{fig:figure-5}B, left). The high correlation in errors leads to a speed up of 4-5 for 1 log unit selectivity optimization and 30-40x for 2 log unit selectivity optimization (Figure~\ref{fig:figure-5}B, right), despite the much higher per target errors.
Quantifying $\rho$ for these calculations enables estimation of $\sigma_{selectivity}$, which is useful for estimating expected error for prospective studies, where the experimental values for $\Delta \Delta G_{selectivity}$ are not yet known. Based on the distribution quantified for $\rho$, the expected $\sigma_{selectivity}$ for the CDK2/CDK9 calculations is between 0.76 and 1.16 kcal/mol (Supp. Figure~\ref{fig:sup-figure-3}), which is in good agreement with the bootstrapped RMSE (Figure~\ref{fig:figure-4}, bottom). For the CDK2/ERK2 calculations, $\sigma_{selectivity}$ is expected to fall between 0.82 kcal/mol and 1.10 kcal/mol (Supp. Figure~\ref{fig:sup-figure-3}), which is also in good agreement with the bootstrapped RMSE (Figure~\ref{fig:figure-4}, top).

\begin{figure}
\begin{fullwidth}
\begin{centering}
\includegraphics[width=1.0\linewidth]{figures/figure5.pdf}
% Need at least one blank line for centering to work.
\end{centering}
\caption{
\label{fig:figure-5}
{\bf Correlation in selectivity prediction errors can be used to accelerate selectivity optimization} \\
({\bf A}) (\emph{left}) The joint posterior distribution of the prediction errors for CDK2 (X-axis) and ERK2 (Y-axis) from the Bayesian graphical model. (\emph{right}) Speedup in selectivity optimization (Y-axis) as a function of correlation coefficient (X-axis). The posterior marginal distribution of the correlation coefficient ($\rho$) is shown in gray, while the expected speed up is shown for 100x (green curve) and 10x (yellow curve) selectivity optimization. The inserted box shows the mean and 95\% confidence interval for the correlation coefficient. The marginal distribution of speedup is shown on the right side of the plot for both 100x (green) and 10x (yellow) selectivity optimization speedups. 
({\bf B}) (\emph{left}) The same as above, with CDK2 (X-axis) and CDK9 (Y-axis). (\emph{right}) As above, for the CDK2/CDK9 calculations.}
\end{fullwidth}
\end{figure}

@@

\begin{figure}[h]
\begin{fullwidth}
\begin{centering}
\includegraphics[width=1.0\linewidth]{figures/supp_figure3.pdf}
% Need at least one blank line for centering to work.
\end{centering}
\caption{
\label{fig:sup-figure-3}
{\bf Correlation reduces the expected error for selectivity predictions} \\
As corelation coefficient $\rho$ increases, $\sigma_{selectivity}$ decreases. The intersection between CDK2/CDK9 $\sigma_{selectivity}$ (green curve) and $\rho$ (black distribution) indicates the range of expected $\sigma_{selectivity}$ values. The intersection for CDK2/ERK $\sigma_{selectivity}$ (blue curve) and $\rho$ (gray distribution) suggests the expected $\sigma_{selectivity}$ range for that set of calculations. 
}
\end{fullwidth}
\end{figure}

>>>>

\paragraph{The CDK2 and CDK9 experimental dataset demonstrates the difficulty in achieving selectivity for closely related kinases}
\todo{I will insert some sentences about the relatedness of the kinases based on Andrea's analysis}
To begin quantifying the correlation of errors in free energy predictions for selectivity, we set out to gather datasets that met a number of criteria. We looked for datasets that contained binding affinity data for a number of kinase targets and ligands, as well as having crystal structures for each target with the same co-crystallized ligand. For the CDK2/CDK9 datatset~\citep{Shao2013-oe}, ligand 12c was cocrystallized with CDK2/cylin A (Figure~\ref{fig:figure-2}A, left) and CDK9/cyclin T (Figure~\ref{fig:figure-2}B, left), work that was published in a companion paper~\citep{Hole2013-sr}. In both CDK2 and CDK9, ligand 12c forms relatively few hydrogen bond interactions with the kinase. Each kinase forms a set of hydrogen bonds between the ligand scaffold and a hinge residue (C106 in CDK9 and L83 in CDK2) that is conserved across all of the ligands in this series. CDK9, which has slightly lower affinity for ligand 12c (Figure~\ref{fig:figure-2}C, right), forms a lone interaction between the sulfonamide of ligand 12c and residue E107. On the other hand, CDK2 forms interactions between the sulfonamide of ligand 12c and residues K89 and H84. The congeneric series of ligands contains a number of challenging perturbations, particularly at substituent point R3 (Figure~\ref{fig:figure-2}C, left). Ligand 12i also presented a challenging perturbation, moving the 1-(piperazine-1-yl)ethanone from the \emph{meta} to \emph{para} location.

@@

\paragraph{The CDK2 and ERK2 dataset achieves higher levels of selectivity for more distantly related kinases}
The CDK2/ERK2 datatset from Blake \emph{et al.,} 2016 also met the criteria described above. Crystal structures for both CDK2 (Figure~\ref{fig:figure-3}A, top) and ERK2 (Figure~\ref{fig:figure-3}B, top) were available with ligand 22 co-crystallized. Of note, CDK2 was not crystallized with cyclin A, despite cyclin A being included in the affinity assay reported in the paper~\citep{Blake2016-su}. CDK2 adopts a DFG-in conformation with the $\alpha$C helix rotated out, away from the ATP binding site and breaking the conserved salt bridge between K33 and E51 (Supp. Figure~\ref{fig:sup-figure-1}A), indicative of an inactive kinase~\citep{Huse2002-ml,Hari:2013dp}. By comparison, the CDK2 structure from the CDK2/CDK9 dataset adopts a DFG-in conformation with the $\alpha$C helix rotated in, forming the ionic bond between K33 and E51 indicative of an active kinase, due to allosteric activation by cyclin A. While missing cyclins have caused problems for free energy calculations in prior work~\todo{is there a good citation for this?}, it is possible that the fully active conformation contributes equally to binding affinity for all of the ligands in the series, and the high accuracy of the potency predictions (Figure~\ref{fig:figure-4}, top left) is the result of fortutious cancellation of errors. The binding mode for this series is similar between both kinases. There is a set of conserved hydrogens bonds between the scaffold of the ligand and the backbone of one of the hinge residues (L83 for CDK2 and M108 for ERK2). The conserved lysine (K33 for CDK2 and K54 for ERK2), normally involved in the formation of a ionic bond with the $\alpha$C helix, forms a hydrogen bond with the scaffold (Figure~\ref{fig:figure-4}A and~\ref{fig:figure-4}B, bottom) in both CDK2 and ERK2. However, in the ERK2 structure, the hydroxyl engages a crystallographic water as well as N154 in a hydrogen bond network that is not present in the CDK2 structure. 
The congenric ligand series features a single subsituent point, with the R groups exposed to the solvent. This helps explain the extremely narrow distribution of selectivities, with a mean selectivity of -1.74 kcal/mol (ERK2 - CDK2) and standard deviation of 0.56 kcal/mol. This suggests that the selectivity is largely driven by the scaffold and unaffected by the R group substitutions.

@@

\paragraph{FEP+ calculations show accurate potency predictions for ERK2/CDK2 and larger errors for CDK2/CDK9}
The FEP+ predictions of single target potencies ($\Delta G$) showed good accuracy for the CDK2 and ERK2 dataset (Figure~\ref{fig:figure-4}, top). Replicate 1 of the calculations in shown in Figure~\ref{fig:figure-4}, with an RMSE of $0.41^{0.71}_{0.13}$ and $0.79^{1.48}_{0.09}$ kcal/mol, respectively. All of the CDK2 potencies were predicted within 1 log unit of the experimental value, while ERK2 had two outliers. The selectivity ($\Delta \Delta G_{selectivity}$) predictions show an RMSE of $0.77^{1.38}_{0.22}$ kcal/mol, with all but one of the predictions falling within 1 log unit of the experimental values (Figure~\ref{fig:figure-4}, top right panel). This was consistent across all three replicates of the calculations (Supp. Figure ~\ref{fig:sup-figure-6}). This consistency across replicates holds true at the individual ligand level as well (Supp. Figure~\ref{fig:sup-figure-8}). Despite the low RMSE for the selectivity predictions, the narrow dynamic range and high uncertainty from experiment and calculation makes it difficult to determine which compounds are more selective than others.

Replicate 1 of the CDK2/CDK9 calculations are shown in the bottom panel of Figure~\ref{fig:figure-4}. The CDK2 and CDK9 datasets show higher errors in the potency predictions, with an RMSE of $1.04^{1.86}_{0.27}$ and $1.79^{2.65}_{0.84}$ kcal/mol respectively. There are a number of outliers that fall outside of 1 log unit from the experimental value for CDK2 and CDK9. While the higher per target errors make predicting potency more difficult, the selectivity predictions show a much lower RMSE of $0.70^{1.06}_{0.30}$ kcal/mol. This suggests that some correlation in the error is leading to fortuitous cancellation of the forcefield error, leading to more accurate than expected predictions of $\Delta \Delta G_{selectivity}$. These results were consistent across all three replicates of the calculation (Supp. Figure ~\ref{fig:sup-figure-4}) as well as each individual ligand (Supp. Figure~\ref{fig:sup-figure-8}).

@@

\paragraph{Correlation of forcefield errors accelerates selectivity optimization}
To quantify the correlation coefficient ($
\rho$) of the forcefield errors in our calculations, we built a Bayesian graphical model to separate the forcefield error from the statistical error, as described in depth in the methods section. Briefly, we modeled the absolute free energy ($G$) of each ligand in each phase (complex and solvent) as in equation~\ref{eq4}. The model was chained to the FEP+ calculations by providing the $\Delta G^{calc}_{phase,ij,target}$ as observed data, as in equation~\ref{eq6}. As in equation, the experimental data was modeled as a normal distribution centered around the true free energy of binding ($\Delta G^{true}_{i,target}$) corrupted by experimental error, which is assumed to be 0.3 kcal/mol from previous work done to quantify the uncertainty in publicly available data~\citep{BROWN2009420}. The reported IC50 values from each dataset were treated as data observations (Equation~\ref{eq12}) and the $\Delta G^{true}_{i,target}$ was assigned a weak normal prior (Equation~\ref{eq13}). The correlation coefficient was calculated for each sample according to equation~\ref{eq9}. 
The correlation coefficient $\rho$ for replicate 1 of the CDK2/ERK2 calculations was quantified to be $0.49^{0.68}_{0.27}$, indicating that the errors are correlated between ERK2 and CDK2 (Figure~\ref{fig:figure-5}A, right), which was consistent with the distributions for $\rho$ in replicates 2 and 3 (Supp. Figure~\ref{fig:sup-figure-7}). The joint marginal distribution of the error ($\epsilon$) for each target is more diagonal than symmetric, which is expected for cases in which $\rho$ is 0.5 (Supp. Figure~\ref{fig:sup-figure-2}). In addition to correlation in the forcefield errors, the high per target accuracy of these calculations allow for a predicted 2-3x speed up for 1 log unit selectivity optimization, and a 20-50x speed up for 2 log unit selectivity optimization (Figure~\ref{fig:figure-5}A, right), in the regime of infinite sampling effort where statistical error is 0.

The CDK2/CDK9 calculations show strong evidence of correlation, with a correlation coefficient of $0.72^{0.83}_{0.58}$ (Figure~\ref{fig:figure-5}B, right) for replicate 1. The rest of the replicates showed strong agreement (Supp. Figure~\ref{fig:sup-figure-5}) The joint marginal distribution of errors is strongly diagonal, which is expected based on the value for $\rho$ (Figure~\ref{fig:figure-5}B, left). The high correlation in errors leads to a speed up of 2-3 for 1 log unit selectivity optimization and 30-40x for 2 log unit selectivity optimization (Figure~\ref{fig:figure-5}B, right), despite the much higher per target RMSE than the CDK2/ERK2 case.

Quantifying $\rho$ for these calculations enables estimation of the forcefield error in the selectivity predictions, $\sigma_{selectivity}$. This is useful for estimating expected error for prospective studies, where the experimental values for $\Delta \Delta G_{selectivity}$ are not yet known. Based on the distribution quantified for $\rho$, the expected $\sigma_{selectivity}$ for the CDK2/CDK9 calculations is $1.18^{1.38}_{0.95}$ kcal/mol (Supp. Figure~\ref{fig:sup-figure-3}), which is in good agreement with the bootstrapped RMSE (Figure~\ref{fig:figure-4}, bottom). For the CDK2/ERK2 calculations, $\sigma_{selectivity}$ is $0.96^{1.14}_{0.75}$ (Supp. Figure~\ref{fig:sup-figure-3}), which is also in good agreement with the bootstrapped RMSE (Figure~\ref{fig:figure-4}, top).

\begin{figure}
\begin{fullwidth}
\begin{centering}
\includegraphics[width=1.0\linewidth]{figures/figure5.pdf}
% Need at least one blank line for centering to work.
\end{centering}
\caption{
\label{fig:figure-6}
{\bf Correlation in selectivity prediction errors can be used to accelerate selectivity optimization} \\
({\bf A}) (\emph{left}) The joint posterior distribution of the prediction errors for CDK2 (X-axis) and ERK2 (Y-axis) from the Bayesian graphical model. (\emph{right}) Speedup in selectivity optimization (Y-axis) as a function of correlation coefficient (X-axis). The posterior marginal distribution of the correlation coefficient ($\rho$) is shown in gray, while the expected speed up is shown for 100x (green curve) and 10x (yellow curve) selectivity optimization. The inserted box shows the mean and 95\% confidence interval for the correlation coefficient. The marginal distribution of speedup is shown on the right side of the plot for both 100x (green) and 10x (yellow) selectivity optimization speedups. 
({\bf B}) (\emph{left}) The same as above, with CDK2 (X-axis) and CDK9 (Y-axis). (\emph{right}) As above, for the CDK2/CDK9 calculations.}
\end{fullwidth}
\end{figure}

\paragraph{Expending more effort to reduce statistical error can improve selectivity optimization speedups}
To this point, we have considered only forcefield error in quantifying the speedup free energy calculations can enable for selectivity optimization, by assuming we are in the range of infinite sampling, where the statistical error for each target is reduced to 0 kcal/mol. To begin understanding how statistical error impacts this speedup, we modified the model of speedup by additional considering the per target statistical error ($\sigma_{stat}$), which we define in Equation~\ref{eq15} such that at the baseline effort, N, $\sigma_{stat}$ is 0.2 kcal/mol. In this definition, it takes 4 times the sampling, or effort, to reduce statistical error by a factor of 2. We assume that statistical error is uncorrelated when propagating to two targets, and that $\sigma_{ff}$ is 0.9 kcal/mol for both targets~\citep{Harder2016-zn, Hauser:2018vz}. As shown in Figure~\ref{fig:figure-6}, expending effort to reduce $\sigma_{stat}$ when $\rho$ is less than 0.5 does not change the expected speedup for the 100x threshold in meaningful way, suggesting that it is not worth running calculations longer than the default protocol in this case. However, when $\rho$ is greeter than 0.5, the curves do start to separate, particularly the 1/4x, 1x and 4x effort curves. This suggests that when the correlation is high, running longer calculations can net improvements in selectivity optimization speed. Interesting, the 16x, 48x and $\infty$ effort curves do not differ greatly from the 4x effort curve, indicating that there are diminishing returns to expending more time running longer calculations.

In order to understand what the current statistical error is for our calculations, we performed three replicates of our calculations, and calculated the standard deviation of the cycle closure $\Delta \Delta G$ for each edge of the map, and compared that value to the cycle closure errors reported for each edge (Supp. Figure~\ref{fig:sup-figure-9}). In general, the standard deviation suggests that the statistical error for our calculations is between 0.1 and 0.3 kcal/mol. While this does not agree well with the cycle closure error (Supp. Figure~\ref{fig:sup-figure-9}), the high variation of the cycle closure errors between replicates of each edge suggest that the standard deviation is a more reliable estimate of what the statistical error for these calculations is.

\begin{figure}
	\begin{fullwidth}
		\begin{centering}
			\includegraphics[width=1.0\linewidth]{figures/figure6.pdf}
			% Need at least one blank line for centering to work.
		\end{centering}
		\caption{
			\label{fig:figure-5}
			{\bf Correlation in selectivity prediction errors can be used to accelerate selectivity optimization} \\
			({\bf A}) (\emph{left}) The joint posterior distribution of the prediction errors for CDK2 (X-axis) and ERK2 (Y-axis) from the Bayesian graphical model. (\emph{right}) Speedup in selectivity optimization (Y-axis) as a function of correlation coefficient (X-axis). The posterior marginal distribution of the correlation coefficient ($\rho$) is shown in gray, while the expected speed up is shown for 100x (green curve) and 10x (yellow curve) selectivity optimization. The inserted box shows the mean and 95\% confidence interval for the correlation coefficient. The marginal distribution of speedup is shown on the right side of the plot for both 100x (green) and 10x (yellow) selectivity optimization speedups. 
			({\bf B}) (\emph{left}) The same as above, with CDK2 (X-axis) and CDK9 (Y-axis). (\emph{right}) As above, for the CDK2/CDK9 calculations.}
	\end{fullwidth}
\end{figure}

@@

\begin{figure}[h]
\begin{fullwidth}
\begin{centering}
\includegraphics[width=1.0\linewidth]{figures/supp_figure3.pdf}
% Need at least one blank line for centering to work.
\end{centering}
\caption{
\label{fig:sup-figure-3}
{\bf Correlation reduces the expected error for selectivity predictions} \\
As corelation coefficient $\rho$ increases, $\sigma_{selectivity}$ decreases. The intersection between CDK2/CDK9 $\sigma_{selectivity}$ (green curve) and $\rho$ (black distribution) indicates the range of expected $\sigma_{selectivity}$ values. The intersection for CDK2/ERK $\sigma_{selectivity}$ (blue curve) and $\rho$ (gray distribution) suggests the expected $\sigma_{selectivity}$ range for that set of calculations. The right side of the plot shows the marginal distribution for CDK2/CDK9 $\sigma_{selectivity}$ (green curve) and CDK2/ERK $\sigma_{selectivity}$ (blue curve). 
}
\end{fullwidth}
\end{figure}
